Analyzing Buildlogs Using Programming by Example

### 2019-05-06 paper/paper.tex
add references to outline

\section{Related Work}
\paragraph{CI Research}
google paper, ing \& os java paper, travistorrent
\paragraph{Analyzing Buildlogs}
maven/java paper
\paragraph{Information Extraction}
prose flashextract

TODO put in proper references to the papers youre surely gonna need here

\section{Background}
program synthesis from example, neccessary theoretical stuff

here all the references to prose theoretical papers

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

>>>>

\section{Related Work}
\paragraph{CI Research}
google paper \cite{seo2014programmers}, ing \& os java paper \cite{vassallo2017a-tale}, travistorrent \cite{beller2017oops}
\paragraph{Analyzing Buildlogs}
maven/java paper \cite{vassallo2018un-break}
\paragraph{Information Extraction}
prose flashextract \cite{le2014flashextract:}, more papers with other approaches of extraction? especially: other extraction from similar data formats

\section{Background}
program synthesis from example, neccessary theoretical stuff,
here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}
